### 2019-02-22 manuscript/introduction.tex
revised first paragraph of Intro

>>>>

Species accumulate around the tree of life at different rates.
The search for traits that explain these differences has been accelerated by dramatic increases in phylogenetic data and, despite some setbacks \citep{maddison_2015, rabosky_2015}, advances in analytical methods \citep{maddison_2007, fitzjohn_2009, goldberg_2012, beaulieu_2016}. % todo more refs: papers with big trees; quasse, bisse-ness, fisse, abc-quasse, maybe hoehna-vs-rabosky
In these studies, it is common to identify a single focal trait and investigate its association with rates of speciation and extinction. % (but see... ?) % refs: there must be some papers that musse on multiple traits? especially for geographic range?
This is problematic for two reasons.
On the biology side, the context in which traits occur can lead to complex interactions, perhaps with other traits that make up an organism or its environment.
On the methods side, excluding other traits that additionally influence diversification can lead to incorrect conclusions about the focal trait \citep{rabosky_2015, beaulieu_2016}.
One approach to this problem is to allow for a `hidden' or unspecified trait in the analysis \citep{beaulieu_2016}. % and an earlier beaulieu? applications of hisse?
This can be effective, but it leaves behind the question of whether the hidden trait corresponds to a real trait that should be sought, or whether it is an approximation of some unknowable heterogeneity, as well as whether interactions between the known and hidden trait were modeled appropriately.
Alternatively, we can simultaneously consider the effects of more than one known trait, especially in systems where multiple traits are suspected to influence diversification, and where interactions between those traits are well understood.
% B: We can then have a good prior, reliable data, and replicate the studies.  E: Agree. But when I tried to add it, I realized hidden models can also be hypothesis-generating, with the purported hidden trait identified in the next clade.
In this paper, we focus on two of the best studied traits in flowering plants, ploidy and breeding system, and investigate their individual and joint effects on diversification.
